# CAMspiracy Analyses

### Preparation

Set the directory of location of this script as the current directory.

```{r wd}
setwd(dirname(rstudioapi::getSourceEditorContext()$path))

rm(list=ls(all=TRUE))
graphics.off()

```

##### Define data

```{r data}
CAMdataset <- "CAMspiracy_data_fixed.txt"

protocolDataset <- "protocol_fixed_15.txt" #  # protocol.txt

consider_Protocol <- TRUE

```

##### Load packages

```{r library, warning=FALSE}
library(shiny)

# library(shinyWidgets)
library(shinyjs)

library(shinyvalidate)

# library(shinycssloaders) %>% withSpinner(color="#0dc5c1")

library(tidyverse)
library(lubridate)

library(magrittr)

library(rjson) # write JSON files
library(jsonlite) # read JSON files



library(igraph)

library(sortable)

library(vroom)
#library(xlsx)


library(irr)


library(stargazer)


library(kableExtra) # APA 7 tables

## for heatmap
library(stats)
library(heatmaply)
library(plotly)
library(RColorBrewer)


library(tm)
library(stopwords) # old function for spell checking

library(visNetwork)
library(wordcloud)


library(moments)

library(psych)
library(rempsyc) # APA tables with nice_table()
library(flextable) # dependency of rempsyc
library(officer) # landscape mode for docx export

library(Cairo) # save CAMs as .png file

library(ggcorrplot)



library(CliquePercolation)

library(qgraph)

```

##### Load functions

```{r functions_CAMapp}
setwd("functions_CAMapp")
dir()


for(i in 1:length(dir())){
  # print(dir()[i])
  source(dir()[i], encoding = "utf-8")
}
rm(i)

```

##### Load data

```{r data, warning=FALSE}
setwd("../data")

read_file(CAMdataset) %>%
  # ... split it into lines ...
  str_split('\n') %>% first() %>%
  # ... filter empty rows ...
  discard(function(x) x == '') -> dat_CAM
# 
# 
raw_CAM <- list()
for(i in 1:length(dat_CAM)){
  raw_CAM[[i]] <- jsonlite::fromJSON(txt = dat_CAM[[i]])
}
rm(i)

### if protocol considered
if(consider_Protocol){
  text <- readLines(protocolDataset, warn = FALSE)
  text <- readLines(textConnection(text, encoding="UTF-8"), encoding="UTF-8")
  
  if (testIfJson(file = text)) {
    protocol <- rjson::fromJSON(file = protocolDataset)
  } else{
    print("Invalid protocol uploaded")
  }
}

setwd("..")

```

### Create CAM files, draw CAMs

Create CAM single files (nodes, connectors, merged)

```{r create_CAM_files}
CAMfiles <- create_CAMfiles(datCAM = raw_CAM, reDeleted = TRUE)

```

Consider protocol.

```{r protocol}
if(consider_Protocol){
  CAMfiles[[1]] <- CAMfiles[[1]][CAMfiles[[1]]$CAM %in% protocol$currentCAMs,]
  CAMfiles[[2]] <- CAMfiles[[2]][CAMfiles[[2]]$CAM %in% protocol$currentCAMs,]
  CAMfiles[[3]] <- CAMfiles[[3]][CAMfiles[[3]]$CAM.x %in% protocol$currentCAMs,]


  tmp_out <- overwriteTextNodes(protocolDat = protocol,
                                nodesDat = CAMfiles[[1]])
  CAMfiles[[1]] <- tmp_out[[1]]
  tmp_out[[2]]
}

```

Draw CAMs

```{r draw_CAMs}
CAMdrawn <- draw_CAM(dat_merged = CAMfiles[[3]],
                     dat_nodes = CAMfiles[[1]],ids_CAMs = "all",
                     plot_CAM = FALSE,
                     useCoordinates = FALSE,
                     relvertexsize = 3,
                     reledgesize = 1)

plot(CAMdrawn[[1]], edge.arrow.size = .7,
     layout=layout_nicely, vertex.frame.color="black", asp = .5, margin = -0.1,
     vertex.size = 10, vertex.label.cex = .9)




tmp_micro <- c("Climate Change")

tmp_Indicators <- compute_indicatorsCAM(drawn_CAM = CAMdrawn,
                                        micro_degree =  tmp_micro,
                                        micro_valence = tmp_micro,
                                        micro_centr_clo = tmp_micro,
                                        micro_transitivity = tmp_micro,
                                        largestClique = FALSE)

```

##### Create Word list

```{r wordlist}
tmp_text <- str_remove_all(string = CAMfiles[[1]]$text,
                           pattern = "_positive$|_negative$|_neutral$|_ambivalent$")

CAMwordlist <- create_wordlist(
  dat_nodes = CAMfiles[[1]],
  dat_merged = CAMfiles[[3]],
  useSummarized = TRUE,
  order = "frequency",
  splitByValence = TRUE,
  comments = TRUE,
  raterSubsetWords = NULL,
  rater = FALSE
)

dat_nodes <- CAMfiles[[1]]
dat_nodes$text <-   dat_nodes$text_summarized
sum(stringr::str_detect(string = dat_nodes$text, pattern = "_positive$|_negative$|_neutral$|_ambivalent$")) < nrow(dat_nodes)

```

#### Still Missing: A bridge between CAMfiles and CliquePercolation

At this point, we need to create adjacency matrices. For each group (high vs. low climate change conspiracy belief) we need a separate matrix in order to determine differences. However, with this type of matrix we have a huge loss of information compared to a weight matrix. Since the aggregated CAM is an unweighted graph, I cannot think of an elegant way to deal with this problem.

```{r matrix}
dat_merged <- CAMfiles[[3]]
dat_nodes <- CAMfiles[[1]]
# ids_CAMs <- NULL
ids_CAMs <- "all"


## check for identical IDs
if(!all(dat_merged$CAM.x %in% dat_nodes$CAM)) {
  cat("Your IDs of the two dataset you specified are not perfectly matching: \n")
  stop("> please respecify the \"dat_merged\" AND / OR \"dat_nodes\" argument")
}

if(!all(ids_CAMs %in% dat_nodes$CAM)) {
  print("aggregate_CAMs: using participant CAM ids")
  dat_merged$CAM.x <- dat_merged$participantCAM.x
  dat_nodes$CAM <-   dat_nodes$participantCAM
}

## check ids_CAMs argument + create ids_CAMs
if(length(ids_CAMs) == 1 && ids_CAMs == "all"){
  ids_CAMs <- unique(dat_merged$CAM.x)
}else if(is.character(ids_CAMs) && !all(ids_CAMs %in% unique(dat_merged$CAM.x))){
  cat("Your specified ids are:", ids_CAMs, ", which is / are not matching the ids of the dataset (seperated by '//'):" ,"\n")
  cat(paste0(unique(dat_merged$CAM.x), collapse = " // "), "\n")
  stop("> Redefine ids")
}


## create subsets:
sel_dat_nodes <- dat_nodes[dat_nodes$CAM %in% ids_CAMs, ]
sel_dat_nodes$value[sel_dat_nodes$value==10] <- 0


## redraw CAMs
sel_drawn_CAM <- draw_CAM(
  dat_merged = dat_merged,
  dat_nodes = dat_nodes,
  ids_CAMs = ids_CAMs,
  plot_CAM = FALSE,
  relvertexsize = 5,
  reledgesize = 1
)

if (any(colnames(sel_dat_nodes) == "text_summarized")) {
  print("text_summarized column identified")
  sel_dat_nodes$text_backup <- sel_dat_nodes$text
  sel_dat_nodes$text <- sel_dat_nodes$text_summarized
}



adjmat <- matrix(data = 0, nrow = length(unique(sel_dat_nodes$text)),
                 ncol = length(unique(sel_dat_nodes$text)))

rownames(adjmat) <- unique(sel_dat_nodes$text)
colnames(adjmat) <- unique(sel_dat_nodes$text)


for(i in 1:length(sel_drawn_CAM)) {
  ## add 1 to the diagonal
  diag(adjmat[rownames(adjmat) %in% V(sel_drawn_CAM[[i]])$label, colnames(adjmat) %in% V(sel_drawn_CAM[[i]])$label]) <-
    diag(adjmat[rownames(adjmat) %in% V(sel_drawn_CAM[[i]])$label, colnames(adjmat) %in% V(sel_drawn_CAM[[i]])$label]) + 1
  
  ## add 1 if edges are connected
  tmp_labels <- cbind(V(sel_drawn_CAM[[i]])$name, V(sel_drawn_CAM[[i]])$label)
  tmp_edges <- as_edgelist(sel_drawn_CAM[[i]])
  
  for (j in 1:nrow(tmp_labels)) {
    tmp_edges[, 1][tmp_edges[, 1] %in% tmp_labels[j, 1]] <-
      tmp_labels[j, 2]
    tmp_edges[, 2][tmp_edges[, 2] %in% tmp_labels[j, 1]] <-
      tmp_labels[j, 2]
  }
  
  for (k in 1:nrow(tmp_edges)) {
    adjmat[rownames(adjmat) == tmp_edges[k, 1], colnames(adjmat) == tmp_edges[k, 2]] <-
      adjmat[rownames(adjmat) == tmp_edges[k, 1], colnames(adjmat) == tmp_edges[k, 2]] + 1
  }
}

```

#### Test Area. Caution: Please be aware of falling objects! Don't forget your safety helmet!

Tutorial: <https://cran.r-project.org/web/packages/CliquePercolation/vignettes/CliquePercolation.html>

Informative paper: \
Lange, J., (2021). CliquePercolation: An R Package for conducting and visualizing results of the clique percolation network community detection algorithm. Journal of Open Source Software, 6(62), 3210, <https://doi.org/10.21105/joss.03210>

-   *k*-cliques = fully connected networks with *k* nodes. The smallest possible k would be *k* = 3. Otherwise, the cliques would be only edges.
-   *I* = For weighted networks, the algorithm has just one intermediate additional step. Specifically, after identifying the k-cliques, they are considered further only if their Intensity exceeds a specified threshold I. The Intensity of a k-clique is defined as the geometric mean of the edge weights.

```{r cp}

W <- Matrix::forceSymmetric(adjmat) # Some kind of matrix (adjacency or weight matrix that is symmetric)
W <- qgraph::qgraph(W, theme = "colorblind", layout = "spring", cut = 0.4) # Just for visualization 

### To run the clique percolation algorithm for weighted networks, we initially need to optimize k and I.

thresholds <- cpThreshold(W, method = "weighted", k.range = c(3,4),
                          I.range = c(seq(0.40, 0.01, by = -0.005)),
                          threshold = c("largest.components.ratio","chi")) # This function may need lots of time to run

##################### Supplementary Analysis: Permutation Test #####################

### Lange (2021): A permutation test, which repeatedly randomly shuffles the edges in the network and recalculates entropy can point out which entropy values are higher than already expected by chance.

threshold <- cpThreshold(W,
  method = "weighted",
  k.range = c(3, 4),
  I.range = seq(0.3, 0.09,-0.01),
  threshold = "entropy"
)

thresholds.permute <- cpPermuteEntropy(W, cpThreshold.object = threshold, seed = 4186)

# -> returning the combinations of k and I that are more surprising than chance

########################################## 

### Run the clique percolation method.

###### Additionally, we enter the optimal k and I values determined via cpThreshold. 

cpk3I.35 <- cpAlgorithm(W, k = 3, method = "weighted", I = 0.35)
cpk4I.27 <- cpAlgorithm(W, k = 4, method = "weighted", I = 0.27)

### Using summary, it is possible to get more detailed information about the communities, shared nodes, and isolated nodes.

summary(cpk3I.35)

### To look at the community size distribution.

cpCommunitySizeDistribution(cpk3I.35$list.of.communities.numbers)

### To actually test whether the distribution for k=3 fits a power-law (i.e., are k=3 and I=.35  the optimal parameters for clique percolation?)

fit_pl_k3I.35 <- cpCommunitySizeDistribution(cpk3I.35$list.of.communities.numbers, test.power.law = TRUE)

### Plotting the solution of the clique percolation algorithm in another network, such that a node represents a community, and the edges between nodes represent the number of nodes that two communities share (i.e., the community graph).

commnetwork <- cpCommunityGraph(cpk3I.35$list.of.communities.numbers,
                                node.size.method = "proportional",
                                max.node.size = 20,
                                theme = "colorblind", layout = "spring", repulsion = 0.4)

```

